% Copyright 2020-2023 Robert Bosch GmbH

% Licensed under the Apache License, Version 2.0 (the "License");
% you may not use this file except in compliance with the License.
% You may obtain a copy of the License at

% http://www.apache.org/licenses/LICENSE-2.0

% Unless required by applicable law or agreed to in writing, software
% distributed under the License is distributed on an "AS IS" BASIS,
% WITHOUT WARRANTIES OR CONDITIONS OF ANY KIND, either express or implied.
% See the License for the specific language governing permissions and
% limitations under the License.

The TestResultDBAccess package offers a flexible and efficient way to interact 
with the database of a test result web application. 

Users can choose between direct database access and REST API access, 
depending on their specific needs and preferences.

\subsection{DBAccessFactory}

The \textbf{DBAccessFactory} class is responsible for creating instances of the 
\textbf{DBAccess} interface based on the specified access method. 

It provides the following method:

\begin{itemize}
    \item \textbf{create(access\_method: str): DBAccess} - Creates an instance 
          of \textbf{DBAccess} based on the specified access method 
          (\pcode{rest} or \pcode{db}).
\end{itemize}

\subsection{DBAccess Interface}

The \textbf{DBAccess} interface defines a set of methods for interacting with 
the database. These methods include:

\begin{itemize}
    \item \textbf{connect(host: str, user: str, passwd: str, database: str)} - 
          Establishes a connection to the database.
    \item \textbf{disconnect()} - Destroys the connection to the database.
    \item Various methods for retrieving, creating, updating, and finishing test 
          result data in the database, such as \textbf{arGetCategories()}, 
          \textbf{sGetLatestFileID()}, \textbf{vCreateTags()}, 
          \textbf{vUpdateResultEndTime()}, and \textbf{vFinishTestResult()}.
\end{itemize}

\subsection{DirectDBAccess}

The \textbf{DirectDBAccess} class implements the \textbf{DBAccess} interface for 
direct database access. 
It provides methods for establishing and destroying connections, as well as 
implementing the various data manipulation methods defined in \textbf{DBAccess}.

\subsection{RestApiDBAccess}

The \textbf{RestApiDBAccess} class implements the \textbf{DBAccess} interface 
for REST API access to the database. 
Similar to \textbf{DirectDBAccess}, it provides methods for connecting, 
disconnecting, and implementing data manipulation methods through the REST API.
